method

### 2022-01-26 06_Paper/ER-ED/method.Rmd
deleted blank spaces

```

>>>>

# import EMG data

datalist_EMG = lapply(list.files(here("04_RawData", "pilot", "ER-ED/EMG/analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

# new empty frame to store files into
data_EMG = data.frame(ID = character(), segment = double(), Corr = double(), 
                     Lev = double())
```
